On the application of microwave acoustic resonant viral inactivation \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}

### 2020-07-17 documents/backup/backup_paper.tex
screw it, good enough.

@@

\supercite{Yang Efficient 2016}[1789 \href{https://doi.org/10.1038/srep18030}{\faExternalLink}]
\supercite{Yang Efficient 2016}[1789 \href{https://doi.org/10.1038/srep18030}{\faExternalLink}]

\supercite{Yang Efficient 2016}[1789 \href{https://doi.org/10.1038/srep18030}{\faExternalLink}]

[Frolich 1968] [Frolich 1980] \textrightarrow \ ([Hung 2014] $\parallel$ [Yang 2015] $\parallel$ [Sun 2017])\footnote{We have not conduc98 \href{https://doi.org/10.2514/3.29363}{\faExternalLink}ently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.

More critically, [Yang 2015] (and, in parallel, [Hung 2014]) theoretically model and then experimentally validate in various strains of Influenza A that - due to this acoustic-resonance effect - the power density levels required to crack the lipid envelope are near the safety limits for continuous exposure to humans.\footnote{Sort of. See below and supplemental.}

@@

For even the RF power limits set by standards organizations appear to be based on the observation that few significant resonance modes exist in biological tissues, and (as we shall see), this is grounded in solid {\it in vitro} (albeit more limited {\it in vivo}) evidence.

@@

\collect{Flagship}

@@

\bibliography{1.bib}{}
\bibliographystyle{plain}
\end{document}

>>>>

\nocite{*}

@@

[Frolich 1968] [Frolich 1980] \textrightarrow \ (\supercite{[Hung reflectarray 2014]}[\cite{hungFocusingReflectarrayIts2014} \href{https://doi.org/10.1002/2014RS005481}{\faExternalLink}] $\parallel$ \supercite{[Yang Efficient 2015]}[\cite{yangEfficientStructureResonance2015} \href{https://doi.org/10.1038/srep18030}{\faExternalLink}] $\parallel$ \supercite{[Sun rod-shaped 2017]}{})\footnote{We have not conducently unlike human cellular structures, as we shall see} - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.

More critically, [\cite{dahlPixelRecursiveSuper2017}] (and, in parallel, [Hung 2014]) theoretically model and then experimentally validate in various strains of Influenza A that - due to this acoustic-resonance effect - the power density levels required to crack the lipid envelope are near the safety limits for continuous exposure to humans.\footnote{Sort of. See below and supplemental.}

@@

For even the RF power limits set by standards organizations appear to be based on the observation that no significant resonance modes exist in biological tissues, and (as we shall see), this is grounded in solid {\it in vitro} (albeit more limited {\it in vivo}) evidence.

@@

@@

\bibliography{references}

\bibliographystyle{}

\end{document}

### 2020-07-17 documents/paper.tex
screw it, good enough.

@@

We've got a thing 
that's called 
Radar Love
We've got a wave
in the air

The phased-array techdemo.

\paragraph{{\Large the gist}}\

The chain of literature 
%
[Fr\"{o}hlich 1968] \textrightarrow \ [Fr\"{o}hlich 1980] \textrightarrow \ [Liu 2009] \textrightarrow \ ([Hung 2014] $\parallel$ [Yang 2015] $\parallel$ [Sun 2017])\footnote{We have not conducted a thorough review; many more papers are probably involved.} apparently culminates in the flagship work we focus on in this paper,

{\it Efficient Structure Resonance Energy Transfer from Microwaves to Confined Acoustic Vibrations in Viruses} [Yang 2015].
%

estabilishes that - unique to certain viruses, and apparently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.

More critically, [Yang 2015] (and, in parallel, [Hung 2014]) theoretically model and then experimentally validate in various strains of Influenza A that - due to this acoustic-resonance effect - the power density levels required to crack the lipid envelope are near the safety limits for continuous exposure to humans.\footnote{Sort of. See below and supplemental.}

@@

\bibliography{flagship}

@@

\bibliography{1.bib}{}
\bibliographystyle{plain}
\end{document}

>>>>

\bibliographystyle{plainnat}

@@

\cite{frohlichLongrangeCoherenceEnergy1968} \textrightarrow \ \cite{frohlichBiologicalEffectsMicrowaves1980} \textrightarrow \ (\cite{hungFocusingReflectarrayIts2014} $\parallel$ \cite{yangEfficientStructureResonance2015} $\parallel$ \cite{sunResonantDipolarCoupling2017})\footnote{We have not conducently unlike human cellular structures, as we shall see} - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.

More critically, [] (and, in parallel, [Hung 2014]) theoretically model and then experimentally validate in various strains of Influenza A that - due to this acoustic-resonance effect - the power density levels required to crack the lipid envelope are near the safety limits for continuous exposure to humans.\footnote{Sort of. See below and supplemental.}

@@

@@

\bibliography{references}

\end{document}
